Trends of SDR in Thessaloniki

### 2023-06-06 Article.Rmd
Commit 2023-06-06 19:17

... site location and aerosols effect...

....describe CS and cloud definition....

@@

<!-- ### Clear sky id --->
In order to estimate the effect of the clouds on the SDR we created three datasets, by characterizing each one-minute measurement with a corresponding sky condition. 
The all-sky conditions, containing all the valid measurements. 
The clear-sky conditions data, where we have inferred that the sky was almost clear of clouds, and the remainder part the data as cloudy sky conditions data (cloud-sky). 
To identify the clear-sky conditions we used the method proposed by @Long2000 and by @Reno2016, that was adapted and configured for the site.

.....
cs - cloud distinction elaborate
......

@@

### Data selection

Due to a significant measurement uncertainty near the horizon, we exclude
all measurements with SZA greater than $`r 90-MIN_ELEVA`^\circ$. 
Moreover, due to some obstructions around the site (hills and buildings), we exclude data with Azimuth angle between 
$35^\circ$ and $120^\circ$ and SZA greater than $80^\circ$.
At those instances, Sun is systematically, not visible by the instrument's location.

To make the measurements comparable throughout the dataset. 
<!-- 1au -->
We adjusted all 1-minute radiometric values to the mean Sun - Earth distance.
<!-- TSI -->
<!-- And, we made all measurements relative to the TSI at 1au, in order to compensate for the Suns intensity variability, using a homogenized timeseries of satellite TSI observations. As a result, we processed all radiation data as a fraction of Suns TSI. -->

### Process and aggregation of radiometric data

>>>>

... site location description and aerosols effect...

@@

<!-- ### Clear sky ID -->
In order to estimate the effect of the clouds on the SDR we created three datasets, by characterizing each one-minute measurement with a corresponding sky condition. 
The all-sky conditions, containing all the valid measurements. 
The clear-sky conditions data, where we have inferred that the sky was almost clear of clouds, and the remainder part the data as cloudy sky conditions data (cloud-sky). 
To identify the clear-sky conditions we used the method proposed by @Long2000 and by @Reno2016, that was adapted and configured for the site.
<!-- CS subjectivity -->
We have to note, that the definition of what constitutes as clear or cloudy sky, has some subjectivity, due to the used method of characterization.
As a result, the details of the definition are site specific, it relies on a combination of threshold of comparisons with ideal actinometric models and statistics on different signal behaviours.

@@

<!-- ### Data selection -->
Due to a significant measurement uncertainty near the horizon, we have to exclude
all measurements with SZA greater than $`r 90-MIN_ELEVA`^\circ$. 
Moreover, due to some obstructions around the site (hills and buildings), we excluded data with Azimuth angle between 
$35^\circ$ and $120^\circ$ with SZA greater than $80^\circ$.
At the latter instances, Sun is systematically, not visible by the instrument's location.
<!-- 1au -->
To make the measurements comparable throughout the dataset. 
We adjusted all 1-minute radiometric values to the mean Sun - Earth distance.
<!-- TSI -->
Subsequently, we made all measurements relative to the TSI at 1au, in order to compensate for the Suns intensity variability, using a homogenized time series of satellite TSI observations.
As a result, we processed all radiation data as a fraction of Suns TSI.

..... cite NOAA TSI .....

## Process and aggregation of radiometric data
